---
title: "Tidy_Tuesday"
author: "Tadeo Aviles Zuniga"
date: "4/4/2022"
output: 
prettydoc::html_pretty:
    theme: architect
    
---

## Introduction 
Tidy Tuesday plot illustrating the top baby names between 1991 and 2000. Attempting this Tidy Tuesday I learned a lot dealing with a much larger data set. I applied tools learned in class to stack multiple plots. Though the data wrangling was inefficient, looks a little messy and redundant, I learned different ways to index, and applied the join() function. I also looked into applying a discrete color palette from a continuous scale which was done by writing (discrete = TRUE). I also used the kbl() function to create a table to visualize the data. 

**Dataset: [Babynames](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-03-22/readme.md)**

```{r setup, include= FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load data, include = FALSE}
#load data
  
library("viridis")          
library(paletteer)
library(kableExtra)
library(prettydoc)
library(dplyr)
library(devtools)
library(tidyverse)
library(ggridges)
library(babynames)
library(ggthemes)
library(patchwork)

```


```{r}
#read in data
bn <- babynames[order(-babynames$prop),] %>% filter(complete.cases(.))
bn_F<-bn %>% group_by(year,sex) %>% #filter out everything that is not a complete row 
 filter(year >= 1990 & year <= 2000 & sex == "F")  
view(bn_F)
```

```{r}

F1 <- bn_F %>% filter (year == "1991") %>% arrange(-n) 
F2 <- bn_F %>% filter (year == "1992")%>% arrange(-n)
F3 <- bn_F %>% filter (year == "1993")%>% arrange(-n)
F4 <- bn_F %>% filter (year == "1994")%>% arrange(-n)
F5 <- bn_F %>% filter (year == "1995")%>% arrange(-n)
F6 <- bn_F %>% filter (year == "1996")%>% arrange(-n)
F7 <- bn_F %>% filter (year == "1997")%>% arrange(-n)
F8 <- bn_F %>% filter (year == "1998")%>% arrange(-n)
F9 <- bn_F %>% filter (year == "1999")%>% arrange(-n)
F0 <- bn_F %>% filter (year == "2000")%>% arrange(-n)

 F1<-F1[1:5,c(1:5)] %>% drop_na()
 F2<-F2[1:5,c(1:5)] %>% drop_na()
 F3<-F3[1:5,c(1:5)] %>% drop_na()
 F4<-F4[1:5,c(1:5)] %>% drop_na()
 F5<-F5[1:5,c(1:5)] %>% drop_na()
 F6<-F6[1:5,c(1:5)] %>% drop_na()
 F7<-F7[1:5,c(1:5)] %>% drop_na()
 F8<-F8[1:5,c(1:5)] %>% drop_na()
 F9<-F9[1:5,c(1:5)] %>% drop_na()
 F0<-F0[1:5,c(1:5)] %>% drop_na()
 
 x<-full_join(F1,F2)
 y<-full_join(F3,F4)
 z<-full_join(F5,F6)
 i<-full_join(F7,F8)
 j<-full_join(F9,F0)
 h<-full_join(x,y)
 l<-full_join(z,i)
 u<-full_join(j,l)
 p<-full_join(u,h)
 
  p <- p %>% arrange(year)
 # print(p)
  view(p)
  
 p[1:50,c("year", "name","prop")] %>% kbl() %>% 
  kable_classic() %>% 
  row_spec(1:50, bold = T, color = "yellow", background = "black")
  
```

### Babynames Plot
```{r coffee, fig.width = 6, fig.height=7, fig.asp=1.2, fig.align='center'}
p %>% 
   ggplot(aes(x = year, 
              y = prop, 
              color = name))+
   geom_point()+
   geom_smooth(method = "lm")+
   geom_jitter()+
   geom_density_ridges(aes(year, y = prop , height = prop, fill = name), 
                                stat = "identity", 
                                scale = 1)+
   labs(title = "Top 5 Female Baby Names between 1991-2000",
        y = "Proportion")+
   #guides(color = guide_legend(title = "Coffee Inflation Rates"))+
   theme_solarized(light = FALSE)+
   theme(
   legend.text = element_text(size = 11),       #title font   
   axis.title.y = element_text(color = "yellow"),#y axis title font 
   axis.title.x = element_text(color = "yellow"),#x axis title font
   axis.text.x = element_text(size = 12, #x axis font 
                              color = "yellow"),
   axis.text.y = element_text(size = 12, #y axis font 
                              color = "yellow"), #y axis color 
   plot.title = element_text(color = "yellow", #plot title color 
                             size = 16))+#plot title size 
   scale_color_viridis(discrete = TRUE, option = "B")+
   scale_fill_viridis(discrete = TRUE)
#bn_M<-bn_1 %>% group_by(sex, year, name) %>% #filter out everything that is not a complete row 
  #filter(year >= 1900 | year <= 1950 | sex == "M") %>% top_n(100) 

#ggsave(here("week_7", "Output", "week_7_good_plot_crb.png"), #saving plot as png
        # width = 7, height = 5) #changing dimensions to 7 x 5 inches

```


