---
title: "Tidy Tuesday College Basketball Revenue"
author: "Tadeo Aviles Zuniga"
date: "4/8/2022"
output: 
prettydoc::html_pretty:
    theme: cayman
    highlight: github
---

## **Introduction** ## 

Tidy Tuesday plot illustrating the top paid universities by sex. Attempting this Tidy Tuesday I learned a lot from the previous dataset. After receiving feedback about improper pipeline practices by profess Silbiger, I was able to extract top data from a larger data set utilizing the group(), arrange(), and slice() functions. In science we often present multiple plots, so I found another method with the package "gridExtra", which allows me to put the plots side by side using nccol(n) or below each other using the nrow(n)to stack multiple plots. Another new tool I utilized was geom_tile() under ggplots. I initially used geom_gapminder() but it suggested geom_tile instead which was pretty cool. A new color pallet I learned was the "scico" package. 

 
 **Dataset: [Sports](https://github.com/rfordatascience/tidytuesday/blob/master/data/2022/2022-03-29/readme.md)**

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r load data, include = FALSE}
library("gridExtra")    
library(reshape)
library(tidyverse)
library(dplyr)
library(here)
library(devtools)
library(ggplot2)
library(ggthemes)
library(gapminder)
library(scico)
library(paletteer)
```

```{r}
#read in Tidy Tuesday data
sports <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2022/2022-03-29/sports.csv')

#Total Revenue 
bball_t <- sports %>% 
 filter(sports == "Basketball") %>% 
  arrange(-total_rev_menwomen) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()

# Woman's Revenue 
bball_w <- sports %>% 
  filter(sports == "Basketball") %>% 
  arrange(-rev_women) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()

#Men's Revenue 
bball_m <- sports %>% 
  filter(sports == "Basketball") %>% 
  arrange(-rev_men) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()

socc_t <- sports %>% 
  filter(sports == "Soccer") %>% 
  arrange(-total_rev_menwomen) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()

socc_m <- sports %>% 
  filter(sports == "Soccer") %>% 
  arrange(-rev_men) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()

socc_w <- sports %>% 
  filter(sports == "Soccer") %>% 
  arrange(-rev_women) %>% 
  slice_head(n = 500) %>% 
  select(year,institution_name, total_rev_menwomen, rev_men, rev_women, state_cd) %>% 
  drop_na()


```

```{r}
#filter and mutate dataframe to create data object coffee

```
```{r rev, fig.width = 6, fig.height=7, fig.asp=1.2, fig.align='center'}
total_revenue <-bball_t[c(1:100),] %>% 
ggplot(aes(x = year , y = institution_name, fill = total_rev_menwomen)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Men and Women's Basketball",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Total Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 12),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
  scale_fill_gradient(low = "#353436",
                      high = "#f6f805",
                      guide = "colorbar")


women_rev <- bball_w[c(1:100),] %>% 
  ggplot(aes(x = year , y = institution_name, fill = rev_women)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Women's Basketball",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Women's Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 12),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
  scale_fill_gradient(low = "#353436",
                      high = "#f6f805",
                      guide = "colorbar")

men_rev <- bball_m[c(1:100),] %>% 
  ggplot(aes(x = year , y = institution_name, fill = rev_men)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Men's Basketball",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Men's Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 12),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
  scale_fill_gradient(low = "#353436",
                      high = "#f6f805",
                      guide = "colorbar")

#ggsave(here("week_7", "Output", "week_7_good_plot_crb.png"), #saving plot as png
       #  width = 7, height = 5) #changing dimensions to 7 x 5 inches

```



```{r plots, fig.width = 6, fig.height=7, fig.asp=1.2, fig.align='center'}
 total_soccer <- socc_t[c(1:100),] %>% 
  ggplot(aes(x = year , y = institution_name, fill = total_rev_menwomen)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Men and Women's Soccer",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Total Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 11),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
        paletteer::scale_fill_paletteer_c("gameofthrones::targaryen")
  

men_soccer <- socc_m[c(1:100),] %>% 
  ggplot(aes(x = year , y = institution_name, fill = rev_men)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Men Soccer",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Men's Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 11),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
        paletteer::scale_fill_paletteer_c("gameofthrones::targaryen")

  
women_soccer <- socc_w[c(1:100),] %>% 
  ggplot(aes(x = year , y = institution_name, fill = rev_women)) +
  geom_tile()+
  labs(x = " Year", 
       y = "Institution",
       title = "Total Revenue in Women's Soccer",
       legend = "Total Revenue")+
  guides(fill = guide_legend(title = "Women's Revenue"))+
  theme_dark()+
  theme(panel.background = element_rect(fill = "black", color = "grey"),
        legend.text = element_text(size = 11),       #title font   
        axis.title.y = element_text(color = "black"),#y axis title font 
        axis.title.x = element_text(color = "black"),#x axis title font
        axis.text.x = element_text(size = 10, #x axis font 
                                   color = "black"),
        axis.text.y = element_text(size = 7, #y axis font 
                                   color = "black"), #y axis color 
        plot.title = element_text(color = "black", #plot title color 
                                  size = 16))+#plot title size )+
        paletteer::scale_fill_paletteer_c("gameofthrones::targaryen")

```

## **Basketball Revenue** ##
### **Description** ###
The plots below represent the top revenue institutions and sex playing basketball. 

```{r print, fig.width = 11, fig.height=13, fig.asp=1.2, fig.align='center'}

grid.arrange(total_revenue, men_rev, women_rev, nrow = 3) 
#grid.arrange(total_soccer, men_soccer, women_soccer, nrow = 3) 

#ggsave(here("week_7", "Output", "week_7_bad_plot_crb.png"), #saving plot as png
         #width = 7, height = 5) #changing dimensions to 7 x 5 inches
```

## **Soccer Revenue** ##
### **Description** ###
The plots below represent the top revenue by institution and sex playing soccer. 
```{r print2, fig.width = 11, fig.height=13, fig.asp=1.2, fig.align='center'}

#grid.arrange(total_revenue, men_rev, women_rev, nrow = 3) 
grid.arrange(total_soccer, men_soccer, women_soccer, nrow = 3) 

#ggsave(here("week_7", "Output", "week_7_bad_plot_crb.png"), #saving plot as png
         #width = 7, height = 5) #changing dimensions to 7 x 5 inches
```